\LARGE \bf Enriching Robot's Actions with Affective Movements

### 2017-03-20 RO-MAN-2017-2/Parts/EmotionalTree.tex
Fixed some Eng. Many pb to solve

Emotional Execution Tree is a connected acyclic graph $G(V,E)$ with $|V|$ vertexes and $|E|$ edges. The root and non-leaf nodes could be of either \textit{parallel} or \textit{sequential} type. Sequential nodes execute one branch after the other. Once all the branches have been executed, it notifies to its predecessor to continue with the execution of other nodes.  The parallel node offers two type of synchronization. one is at action and the other at emotion. This distinction between action and emotion synchronization enables the possibility to change emotion parameter without affecting the action. done could be one out of four different sub-types: (i) action and emotion synchronous, (ii) action synchronous and emotion asynchronous, (iii) action asynchronous and emotion synchronous, or (iv) action and emotion asynchronous. 
 Action synchronous means that each time that a parallel node receives a ``finish'' notification (i.e., success or failure), it will broadcast the message to all nodes that derived it and to its predecessor, which will stop their execution.

 If a sequence node receives a finish message, it will execute the next branch. When all branches have been executed, it communicates the end of the action. On the other hand, emotion synchronous means that each time that a node (either sequence or parallel) receives an emotion synchronization message, it will propagate the message to all branches to move to the consecutive emotional expression. If a node is principal and it has finished to execute all actions, it will notify its predecessor.

This distinction creates the possibility to synchronize emotional changes without affecting the normal execution of an action and it also enables synchronization among parallel actions. Finally, leaf nodes could only be simple action nodes that have been implemented in the system. Any node can belong to one of two levels: principal or  secondary. If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary node cannot propagate any message to its predecessor. This enables the possibility to have actions that are the ones to command over the others. 
Compound actions are implemented combining all type of nodes.

>>>>

Emotional Execution Tree is a connected acyclic graph $G(V,E)$ with $|V|$ vertexes and $|E|$ edges. The root and non-leaf nodes could be of either \textit{parallel} or \textit{sequential} type. Sequential nodes execute one branch after the other. Once all the branches have been executed, it notifies to its predecessor to continue with the execution of other nodes. The parallel node offers two types of synchronization: one is at action and the other at emotion. This distinction between action and emotion synchronization enables the possibility to change emotion parameter without affecting the action. %TODO ???? 
done could be one out of four different sub-types: (i) action and emotion synchronous, (ii) action synchronous and emotion asynchronous, (iii) action asynchronous and emotion synchronous, or (iv) action and emotion asynchronous. 
Action synchronous means that each time that a parallel node receives a ``finish'' notification (i.e., success or failure), it will broadcast the message to all nodes that derived it and to its predecessor %TODO ????
, which will stop their execution.

If a sequence node receives a finish message, it will execute the next branch. When all branches have been executed, it communicates the end of the action.

Emotion synchronous means that each time that a node (either sequence or parallel) receives an emotion synchronization message, it will propagate the message to all branches to move to the consecutive emotional expression. If a node is principal and it has finished to execute all actions, it will notify its predecessor. %TODO Not clear at all 
 This distinction creates the possibility to synchronize emotional changes without affecting the normal execution of an action and it also enables synchronization among parallel actions.

Finally, leaf nodes could only be simple action nodes that have been implemented in the system. Any node can belong to one of two levels: principal or secondary. If a node is principal, it will notify its predecessor about the messages that it has received, while the secondary node cannot propagate any message to its predecessor. This enables the possibility to have actions that have priority on others. 
Compound actions are implemented combining all type of nodes.
